Analysis-ready VCF at Biobank scale using Zarr

### 2024-06-07 paper.tex
Tweak formatting for preprint
Improve typesetting of the URLs

%%% Journal toggle; only specific options recognised.
%%% (Only "gigascience" and "general" are implemented now. Support for other journals is planned.)
\journal{gigascience}

@@

% Local definitions to systematise tool naming
\newcommand{\sgapi}[1]{\texttt{#1}}
\newcommand{\toolname}[1]{\texttt{#1}}
\newcommand{\sgkit}{\texttt{sgkit}}

@@

The VCF Zarr specification is general and can be mapped to 
file formats such as \toolname{plink}~\citep{purcell2007plink,chang2015second}
and BGEN~\citep{band2018bgen} with some minor extensions.

>>>>

%%% Journal toggle; only specific options recognised.
%%% (Only "gigascience" and "general" are implemented now. Support for other journals is planned.)
\journal{preprint}

@@

@@

The VCF Zarr specification is general and can be mapped to 
file formats such as PLINK~\citep{purcell2007plink,chang2015second}
and BGEN~\citep{band2018bgen} with some minor extensions.
